The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-06-04 manuscript/manuscript.tex
Push before add John's edits

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations. \textcolor{red}{[More reference to be added, such as positive evolution for Merloni et al. and other high-z studies such as Peng, non-evolution for Mechtley et al. Xuheng also need to also mention the observables some are stellar mass while others are velocity dispersion.
]}It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.

@@

\section{Experimental design}
\label{sec:data}
%Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. 
We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
\begin{enumerate}
\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break, given their redshift range.
\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
\end{enumerate}

@@

Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
The bolometric luminosities presented in \citet{Schulze2018} enable us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$ and select the sample which meets our selection window, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.

@@

%\subsection{Black hole mass and Eddington ratios}
\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

@@

\begin{eqnarray}
\label{eq:Ha}
\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) ,
\end {eqnarray}

@@

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) .
\end {eqnarray}

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. 14/32 systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged value for log(\mbh). \textcolor{blue}{3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}}.

We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{Inferred BH properties for the 32 systems} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{4}{c}{using emission line \halpha}&
  \multicolumn{4}{c}{using emission line \hbeta} \\
  \cline{2-5}  \cline{6-9} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& (log$\lambda$)&
\colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}&
\colhead{(8)}& \colhead{(9)}
}
\startdata 
CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
The typical uncertainty level for FWHM and $\log(\lambda \rm L)$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
}
\end{deluxetable*}

@@

Multi-band information provides the spectral energy distributions (SED) at a more precise level. 21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}. Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population %to the stellar mass budget 
which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calcualtions.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$. Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\caption{\label{fig:AGN_decomp} 
Figure illustrates the inference for the 32 objects based on the WFC3 images.
In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID. In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom). The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects). Note that the one-dimensional surface brightness profiles are only for illustration purposes. The actual fitting is based on the two-dimensional images. The remaining 31 objects of the sample are shown in appendix A.
}}
\end{figure*}

@@

The inference of the host properties is weighted by eight top-ranked PSFs. With a smaller amount of PSFs, one would possibly underestimate the uncertainties. To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.

@@

{\color{blue} 
Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.

@@

We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample. We doubt whether the positivity of $\gamma$ stems from the four outliers (i.e., the top-four systems in Figure~\ref{fig:MM}). We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample. As a result, we obtain that $\gamma  = 0.55 \pm 0.29$, indicating the positive evolution trend become weaker but still exists, as shown in Figure~\ref{fig:MM_restsample}.

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
\caption{\label{fig:MM_restsample} 
Same as Figure~\ref{fig:MM-vz}, left, but excluding the 4 outliers systems. The result shows the evolution still exist among the other 28 AGN sample.
}
\end{figure}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost\ relation, evolution-corrected]
{\includegraphics[height=0.4\textwidth]{fig/MBH-L_ev.pdf}}&
\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
{\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}}\\
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:ML-vz} 
Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
\end{figure*}

>>>>

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass and \mbh-\sigstar relations. \textcolor{blue}{In addition, based on spectroscopic information, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components, finding a positive evolution of black holes to the galaxies in their correlation.
This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars and limited size of the sample. For example, some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}. In addition, once considering the selection effect \citet{Mechtley2012, Schulze2014}, the observed apparent offset at high redshift is fully consistent with no intrinsic offset.}

@@

\section{Experimental design}
\label{sec:data}
%Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. 
We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
\begin{enumerate}
\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break and below the broad \halpha\ line (6563 \angstrom) given their redshift range.
\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
\end{enumerate}

@@

Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
The bolometric luminosities presented in \citet{Schulze2018} help us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.

@@

%\subsection{Black hole mass and Eddington ratios}
\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. We also control the sample to have higher Eddington ratios when their \mbh\ is lower, to guarantee the AGN activity. For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

@@

\begin{eqnarray}
\label{eq:Ha}
\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) ,
\end {eqnarray}

@@

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) .
\end {eqnarray}

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. {\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha emission line, to assure they are self-consistent.
%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.

We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}. 
}

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{Inferred BH properties for the 32 systems} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{4}{c}{using emission line \halpha}&
  \multicolumn{4}{c}{using emission line \hbeta} \\
  \cline{2-5}  \cline{6-9} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& (log$\lambda$)&
\colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}&
\colhead{(8)}& \colhead{(9)}
}
\startdata 
CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
The typical uncertainty level for FWHM and $\log(\lambda \rm L)$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
}
\end{deluxetable*}

@@

Multi-band information provides the SED at a more precise level. 21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}. Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population %to the stellar mass budget 
which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We also test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
}}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio\footnote{We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.} in Figure~\ref{fig:flux_r_n_corner}.

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\caption{\label{fig:AGN_decomp} 
Figure illustrates the inference for the 32 objects based on the WFC3 images.
In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID. In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom). The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects). Note that the one-dimensional surface brightness profiles are only for illustration purposes. The actual fitting is based on the two-dimensional images. The remaining 31 objects of the sample are shown in Appendix~\ref{sec:restsample}.
}}
\end{figure*}

@@

The inference of the host properties is weighted by eight top-ranked PSFs. The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference. To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.

@@

Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.

@@

We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample. We doubt whether the positivity of $\gamma$ stems from the three outliers (i.e., the top-three systems in Figure~\ref{fig:MM}). We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample. As a result, we obtain that $\gamma  = 0.55 \pm 0.29$, indicating the positive evolution trend become weaker but still exists, as shown in Figure~\ref{fig:MM_restsample}.

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
\caption{\label{fig:MM_restsample} 
Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
}
\end{figure}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost\ relation, evolution-corrected]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:ML-vz} 
Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
\end{figure*}

{\color{blue}
\subsection{The origin of the offset}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}
